Fast Hyper-Parameter Selection for Graph Kernels via Subsampling and\\Multiple Kernel Learning

### 2016-11-26 paper.tex
Switched one reference

\begin{abstract}
Kernel for structures are generally characterized by a number of hyper-parameter which need to be tuned. Moreover, different types of kernels can be used and the best choice usually depends on data. The hyper-parameter setting is a time-consuming step. One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyper-parameters settings. However, this solution still requires the computation of many large kernel matrices. In this paper we propose a subsampling method to efficiently select a small number of kernels which need to be actually computed. Finally, we give empirical evidence that the method proposed is far more efficient than the other approaches while maintaining similar results in terms of AUC.
\end{abstract}

@@

With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
A possible alleviation to this problem has been proposed in~\cite{Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid. This step can also be time consuming, especially when dealing with data in a structured form.

@@

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014,Castro2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
$
	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
$
with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

@@

\section{Experimental Assessment}
We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016,Shervashidze2011} for a more detailed description).
%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
%{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
%[...].
%All the nodes are labeled and there are no self loops.}
%
The kernels used in our experiments are: all NSPDK combinations with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$, all ODDST combinations with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, all WL with $h \in \{0,1\dots9\}$.
In all models, we considered kernels calculated in less that 1 hour, rejecting others.
The baselines used to compare our method consist on a SVM with kernels (a)\kval: the kernel is the one which has the best validation score, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: the kernel is a combination of all base kernels using EasyMKL.
For each baseline, the computation of all kernels is required.
The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.

>>>>

\begin{abstract}
Kernels for structures are generally characterised by a number of hyper-parameters which need to be tuned. Moreover, different types of kernels can be used and the best choice usually depends on data. The hyper-parameter setting is a time-consuming step. One option proposed to overcome this problem is to use the Multiple Kernel Learning approach and generate a kernel which is a combination of different types of kernels and different hyper-parameters settings. However, this solution still requires the computation of many large kernel matrices. In this paper we propose a subsampling method to efficiently select just a small number of kernels which need to be actually computed. Finally, we give empirical evidence that the method proposed is far more efficient than the other approaches while maintaining similar results in terms of AUC.
\end{abstract}

@@

With this approach, a learning procedure has to be performed for each hyper-parameter combination, possibly making it very time consuming.
A possible alleviation to this problem has been proposed in~\cite{FabioAiolliMicheleDonini2015,Massimo2016}, where Multiple Kernel Learning (MKL) has been used for combining different kernel matrices in a single learning procedure, instead of selecting the best parameters configuration.
However, in the case of kernel algorithms, a different kernel matrix has to be computed for each kernel and for each of its hyper-parameters values in the grid. This step can also be time consuming, especially when dealing with data in a structured form.

@@

\subsection{Multiple Kernel Learning}
\label{MKL}
MKL \cite{Gonen2011} is one of the most popular paradigms used to learn kernels in real world applications \cite{Bucak2014}. % Zien2007,Wang2015a,Sun
The kernels generated by these techniques are combinations of a prescribed set of basic kernels $\KK_1,...,\KK_R$ with a constraint in the form:
$
	H_R^q = \{ \xx \mapsto \textbf{w} \cdot \pphi_\KK(\xx) : \KK = \sum_{r=1}^R \eta_r \KK_r, \mmu \in \Psi_q, \|\textbf{w}\|_2 \leqslant 1 \}
$
with $\Psi_q = \{ \mmu : \mmu \succcurlyeq 0, \| \mmu \|_q = 1 \}$ and considering the function $\pphi_\KK$ as the feature mapping from the input space to the feature space. The value $q$ being the kind of mean used, is typically fixed to $1$ or $2$.

@@

\section{Experimental Assessment}
We conducted our experiments on several real-world binary datasets, that are MUTAG, CPDB, GDD, AIDS, NCI1, NCI109, CAS (see \cite{DaSanMartino2016,Shervashidze2011} for a more detailed description).
%AIDS~\cite{Weislow1989a}, CAS\footnote{http://cheminformatics.org/datasets/bursi/},
%CPDB~\cite{Helma2004a}, NCI1~\cite{Wale2006} and GDD~\cite{dobson2003}.
%The first four datasets contain chemical particles encoded in graph form, while the latter encodes proteins.
%{\color{red} The AIDS dataset contains chemical compounds (encoded in graph form), labeled according to their antiviral activity; CAS and CPDB store compounds labeled according to their mutagenicity; NCI1 and NCI109 consist of chemical compounds screened for activity against non-small lung cancer cells; GDD is composed of X-ray crystal structures of proteins; MUTAG contains %MUTAG serve per far vedere che funziona bene anche su dataset piccolissimi
%[...].
%All the nodes are labeled and there are no self loops.}
%
The kernels used in our experiments are:  NSPDK  with $h \in \{0,1\dots9\}$ and $d \in \{0,1\dots9\}$,  ODD$_{ST}$ with $h \in \{0,1\dots9\}$ and $\lambda \in \{0.5, 0.7,0.8\dots1.2,1.4,1.6,1.8\}$, WL with $h \in \{0,1\dots9\}$.
In all models, we considered kernels calculated in less that 1 hour, rejecting others.
The baselines used to compare our method consist on a SVM with kernels (a)\kval: the kernel is the one which has the best validation score, (b)\ksum: the kernel is the average of all base kernels, (c)\kmkl: the kernel is a combination of all base kernels using EasyMKL.
For each baseline, the computation of all kernels is required.
The hyperparameters are chosen using a nested 10-fold CV procedure, and they are $C\in\{2^i, i:-3\dots6\}$, and $\Lambda\in\{0,0.1\dots1\}$ for \kmkl.
